Goals and Tasks

### 2020-05-04 README.Rmd
test

* Supervisor: Thomas Kneib
* Students: Johannes, Levin, Sebastián
* Tasks: Parameter estimation and variable selection using the boosting ensemble learning algorithm

## Tasks

>>>>

* Supervisor: Thomas Kneib
* Students: Johannes, Levin, Sebastián
* Topic: Parameter estimation and variable selection using the boosting ensemble learning algorithm

## Tasks 
ignore this subheader
